---
title: "Market-Side Data Analysis"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-location: body
    toc-depth: 3
    number-sections: true
execute:
  echo: false
---

```{r setup}
#| echo: false
#| output: false
library(tidyverse)
library(dplyr)
library(MASS)
library(ggrepel)
library(forecast)
library(openxlsx)
library(ggridges)
library(tidyr)
library(cowplot)
library(ggcorrplot)
library(ggforce)
library(RColorBrewer)
library(rJava)
library(xlsxjars)
library(xlsx)
library(readxl)
library(patchwork)
library(colourpicker)
library(lubridate)
options(scipen = 10)
```

```{r config}
# Set reporting window: [date_last_mon, date_this_mon)
date_last_mon <- as.POSIXct("2023-12-18", tz = "UTC")
date_this_mon <- date_last_mon + 7 * 24 * 3600

source("daily_report_functions.R")
```

## Sales Data

```{r direct-sales}
# --- Direct (self-operated) ticketing channel ---
da |>
  filter(
    项目 != "测试",
    地址信息 != "测试",
    下单时间 >= as.POSIXct("2023-08-12 00:00:00", tz = "UTC")
  ) |>
  mutate(剧目 = mark_musicals(项目)) |>
  filter(剧目 != "test") |>
  mutate(
    场次      = as.character(开始时间),
    渠道类型  = "自营",
    渠道明细  = mark_from(分销码, 下单时间)[, 1],
    动作日期  = mark_from(分销码, 下单时间)[, 2],
    动作类型  = mark_from(分销码, 下单时间)[, 3],
    实收      = 结算金额,
    张数      = 1,
    地址      = 地址信息,
    收货人手机 = as.character(收货人手机)
  ) |>
  mutate(
    渠道类型 = mark_qudao_zy(动作类型),
    实收     = 实收 * as.numeric(mark_piaoti_zy(渠道类型, 渠道明细, "MA", 票价))
  ) |>
  dplyr::select(
    剧目, 场次, 下单时间, 渠道类型, 渠道明细,
    动作日期, 动作类型, 票价, 实收, 张数,
    收货人姓名, 收货人手机, 地址
  ) -> da_edit
```

```{r distributor-sales}
# --- Distributor (system) ticketing channel ---
da_fenxiao |>
  filter(!is.element(项目, c("测试站票项目", "音乐剧《玛蒂尔达》周边", "《摇滚莫扎特》周边"))) |>
  filter(场地 != "test") |>
  mutate(剧目 = mark_musicals(项目)) |>
  # Patch missing referral codes caused by a known system outage period
  mutate(分销码 = if_else(
    is.element(项目, "法国音乐剧《摇滚莫扎特》中文版【北京预演场】-诺基亚"),
    "KHvDKHvNJY", 分销码
  )) |>
  mutate(分销码 = if_else(
    is.element(项目, "法国音乐剧《摇滚莫扎特》中文版【北京预演场】0912-0918") &
      is.element(分销码, c("-", "QMvGZHvAZ")),
    "KHvDKHvNJY", 分销码
  )) |>
  mutate(
    场次      = as.character(开始时间),
    渠道类型  = "分销-系统",
    渠道明细  = mark_from_name(分销码),
    地址      = 地址信息,
    收货人手机 = as.character(收货人手机),
    票价      = mark_fenxiao_price(票种)[, 1],
    张数      = mark_fenxiao_price(票种)[, 2]
  ) |>
  mutate(
    渠道类型 = mark_piaoti_fx(渠道明细, "MA", 票价)[, 1],
    实收     = 结算金额 * as.numeric(mark_piaoti_fx(渠道明细, "MA", 票价)[, 2])
  ) |>
  dplyr::select(
    剧目, 场次, 下单时间, 渠道类型, 渠道明细,
    票价, 实收, 张数, 收货人姓名, 收货人手机, 地址
  ) -> da_fenxiao_edit
```

```{r merge-sales}
# Combine both channels and annotate project/venue from session datetime
da_for_market <-
  da_edit |>
  bind_rows(da_fenxiao_edit) |>
  mutate(
    动作日期 = coalesce(动作日期, ""),
    项目     = mark_project(场次, 剧目)[, 1],
    剧场     = mark_project(场次, 剧目)[, 2]
  )
```

## WeChat Subscription Account (订阅号)

### Follower Count

```{r wx-sub-fans}
path         <- list.files("E:/实习工作/数据/市场端数据分析/七幕-订阅号", full.names = TRUE)
path_user    <- path[str_detect(path, "user")]
path_article <- path[!str_detect(path, "user")]
```

```{r wx-sub-fans-load}
# Files must be opened and re-saved before reading (Excel format quirk)
da_wx_fan_num <- map_dfr(path_user, function(f) {
  tmp <- readxl::read_xls(f)
  tmp[-c(1, 2), ] |> `colnames<-`(tmp[1, ])
}) |>
  mutate(日期 = as.POSIXct("2023-01-01", tz = "UTC") + (as.numeric(时间) - 44927) * 3600 * 24) |>
  dplyr::select(-时间) |>
  relocate(日期)
```

### Article Performance

```{r wx-sub-articles}
da_wx_article <- map_dfr(path_article, readxl::read_xls) |>
  mutate(发表时间 = as.POSIXct(发表时间, format = "%Y%m%d", tz = "UTC")) |>
  arrange(发表时间)
```

## WeChat Service Account (服务号)

### Follower Count

```{r wx-svc-fans}
path         <- list.files("E:/实习工作/数据/市场端数据分析/七幕-服务号", full.names = TRUE)
path_user    <- path[str_detect(path, "user")]
path_article <- path[!str_detect(path, "user")]

da_wx_fwh_fan_num <- map_dfr(path_user, function(f) {
  tmp <- readxl::read_xls(f)
  tmp[-c(1, 2), ] |> `colnames<-`(tmp[1, ])
}) |>
  mutate(日期 = as.POSIXct("2023-01-01", tz = "UTC") + (as.numeric(时间) - 44927) * 3600 * 24) |>
  dplyr::select(-时间) |>
  relocate(日期)
```

### Article Performance

```{r wx-svc-articles}
da_wx_fwh_article <- map_dfr(path_article, readxl::read_xls) |>
  mutate(发表时间 = as.POSIXct(发表时间, format = "%Y%m%d", tz = "UTC")) |>
  arrange(发表时间)
```

### Combined WeChat Account Summary

```{r wx-combined-current-fans}
# Latest follower count (day before this_mon)
da_wx_tmp1 <-
  bind_rows(
    da_wx_fan_num    |> mutate(账号 = "七幕-订阅号"),
    da_wx_fwh_fan_num |> mutate(账号 = "七幕人生-服务号")
  ) |>
  filter(日期 >= date_this_mon - 3600 * 24, 日期 < date_this_mon) |>
  dplyr::select(粉丝数 = 累积关注人数, 账号) |>
  mutate(粉丝数 = as.numeric(粉丝数))
```

```{r wx-combined-fan-change}
# Net follower change over the reporting week
da_wx_tmp2 <-
  bind_rows(
    da_wx_fan_num    |> mutate(账号 = "七幕-订阅号"),
    da_wx_fwh_fan_num |> mutate(账号 = "七幕人生-服务号")
  ) |>
  filter(日期 >= date_last_mon, 日期 < date_this_mon) |>
  group_by(账号) |>
  summarise(上周粉丝数变化 = sum(as.numeric(新关注人数)) - sum(as.numeric(取消关注人数)))
```

```{r wx-combined-content}
# Content metrics for the reporting week
da_wx_tmp3 <-
  bind_rows(
    da_wx_article    |> mutate(账号 = "七幕-订阅号"),
    da_wx_fwh_article |> mutate(账号 = "七幕人生-服务号")
  ) |>
  filter(发表时间 >= date_last_mon, 发表时间 < date_this_mon) |>
  group_by(账号) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(as.numeric(总阅读次数)),
    总互动量 = "-",
    总分享   = sum(as.numeric(总分享次数))
  )
```

```{r wx-summary-merge}
da_wx_summary <-
  da_wx_tmp1 |>
  full_join(da_wx_tmp2, by = "账号") |>
  full_join(da_wx_tmp3, by = "账号") |>
  mutate(
    平台     = "微信",
    内容数目 = coalesce(内容数目, 0L),
    总观看量 = coalesce(总观看量, 0),
    总互动量 = coalesce(总互动量, "0"),
    总分享   = coalesce(总分享, 0)
  )
```

## WeChat Video Account (视频号)

### Follower Count

```{r wxvideo-fans}
path      <- list.files("E:/实习工作/数据/市场端数据分析/七幕-视频号", full.names = TRUE)
path_user <- path[str_detect(path, "关注者增长详情数据")]
path_video <- path[!is.element(path, path_user)]

# Files must be opened and re-saved before reading
da_wxsp_fan_num <- map_dfr(path_user, function(f) {
  tmp <- read.csv(f)
  tmp[-c(1, 2), ] |> `colnames<-`(tmp[2, ]) |> `rownames<-`(NULL)
}) |>
  mutate(时间 = as.POSIXct(时间, format = "%Y/%m/%d", tz = "UTC"))

da_wxsp_tmp1 <-
  da_wxsp_fan_num |>
  filter(时间 >= date_this_mon - 3600 * 24, 时间 < date_this_mon) |>
  dplyr::select(粉丝数 = 关注者总数) |>
  mutate(粉丝数 = as.numeric(粉丝数))

da_wxsp_tmp2 <-
  da_wxsp_fan_num |>
  filter(时间 >= date_last_mon, 时间 < date_this_mon) |>
  summarise(上周粉丝数变化 = sum(as.numeric(新增关注)) - sum(as.numeric(取消关注))) |>
  mutate(上周粉丝数变化 = as.numeric(上周粉丝数变化))
```

### Video Performance

```{r wxvideo-content}
da_wx_video <- map_dfr(path_video, read.csv) |>
  mutate(发布时间 = as.POSIXct(发布时间, format = "%Y/%m/%d", tz = "UTC"))

da_wxsp_tmp3 <-
  da_wx_video |>
  filter(发布时间 >= date_last_mon, 发布时间 < date_this_mon) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(播放量),
    总互动量 = sum(推荐) + sum(喜欢) + sum(评论量),
    总分享   = sum(分享量)
  )

da_wx_video_summary <-
  da_wxsp_tmp1 |>
  bind_cols(da_wxsp_tmp2) |>
  bind_cols(da_wxsp_tmp3) |>
  mutate(账号 = "七幕-视频号", 平台 = "微信", 总互动量 = as.character(总互动量))
```

## Training Subscription Account (培训-订阅号)

```{r px-sub-fans}
path         <- list.files("E:/实习工作/数据/市场端数据分析/培训-订阅号", full.names = TRUE)
path_user    <- path[str_detect(path, "user")]
path_article <- path[!str_detect(path, "user")]

da_px_fan_num <- map_dfr(path_user, function(f) {
  tmp <- readxl::read_xls(f)
  tmp[-c(1, 2), ] |> `colnames<-`(tmp[1, ])
}) |>
  mutate(日期 = as.POSIXct("2023-01-01", tz = "UTC") + (as.numeric(时间) - 44927) * 3600 * 24) |>
  dplyr::select(-时间) |>
  relocate(日期)

da_px_article <- map_dfr(path_article, readxl::read_xls) |>
  mutate(发表时间 = as.POSIXct(发表时间, format = "%Y%m%d", tz = "UTC")) |>
  arrange(发表时间)
```

```{r px-summary}
da_px_tmp1 <-
  da_px_fan_num |>
  mutate(账号 = "七幕少儿剧团-订阅号") |>
  filter(日期 >= date_this_mon - 3600 * 24, 日期 < date_this_mon) |>
  dplyr::select(粉丝数 = 累积关注人数, 账号) |>
  mutate(粉丝数 = as.numeric(粉丝数))

da_px_tmp2 <-
  da_px_fan_num |>
  mutate(账号 = "七幕少儿剧团-订阅号") |>
  filter(日期 >= date_last_mon, 日期 < date_this_mon) |>
  group_by(账号) |>
  summarise(上周粉丝数变化 = sum(as.numeric(新关注人数)) - sum(as.numeric(取消关注人数)))

da_px_tmp3 <-
  da_px_article |>
  mutate(账号 = "七幕少儿剧团-订阅号") |>
  filter(发表时间 >= date_last_mon, 发表时间 < date_this_mon) |>
  group_by(账号) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(as.numeric(总阅读次数)),
    总互动量 = "-",
    总分享   = sum(as.numeric(总分享次数))
  )

da_px_summary <-
  da_px_tmp1 |>
  full_join(da_px_tmp2, by = "账号") |>
  full_join(da_px_tmp3, by = "账号") |>
  mutate(
    平台     = "微信",
    内容数目 = coalesce(内容数目, 0L),
    总观看量 = coalesce(总观看量, 0),
    总互动量 = coalesce(总互动量, "0"),
    总分享   = coalesce(总分享, 0)
  )
```

## Training Video Account (培训-视频号)

```{r pxvideo}
path       <- list.files("E:/实习工作/数据/市场端数据分析/培训-视频号", full.names = TRUE)
path_user  <- path[str_detect(path, "关注者增长详情数据")]
path_video <- path[!is.element(path, path_user)]

da_pxsp_fan_num <- map_dfr(path_user, function(f) {
  tmp <- read.csv(f)
  tmp[-c(1, 2), ] |> `colnames<-`(tmp[2, ]) |> `rownames<-`(NULL)
}) |>
  mutate(时间 = as.POSIXct(时间, format = "%Y/%m/%d", tz = "UTC"))

da_pxsp_tmp1 <-
  da_pxsp_fan_num |>
  filter(时间 >= date_this_mon - 3600 * 24, 时间 < date_this_mon) |>
  dplyr::select(粉丝数 = 关注者总数) |>
  mutate(粉丝数 = as.numeric(粉丝数))

da_pxsp_tmp2 <-
  da_pxsp_fan_num |>
  filter(时间 >= date_last_mon, 时间 < date_this_mon) |>
  summarise(上周粉丝数变化 = sum(as.numeric(新增关注)) - sum(as.numeric(取消关注))) |>
  mutate(上周粉丝数变化 = as.numeric(上周粉丝数变化))

da_px_video <- map_dfr(path_video, read.csv) |>
  mutate(发布时间 = as.POSIXct(发布时间, format = "%Y/%m/%d", tz = "UTC"))

da_pxsp_tmp3 <-
  da_px_video |>
  filter(发布时间 >= date_last_mon, 发布时间 < date_this_mon) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(播放量),
    总互动量 = sum(推荐) + sum(喜欢) + sum(评论量),
    总分享   = sum(分享量)
  )

da_px_video_summary <-
  da_pxsp_tmp1 |>
  bind_cols(da_pxsp_tmp2) |>
  bind_cols(da_pxsp_tmp3) |>
  mutate(账号 = "七幕少儿剧团-视频号", 平台 = "微信", 总互动量 = as.character(总互动量))
```

## Cross-Platform Follower Data (Weibo / Bilibili / Douyin / XHS)

```{r cross-platform-path}
# Shared workbook covering Weibo, Bilibili, Douyin, and Xiaohongshu
path_wb_bili_xhs <- "E:/实习工作/数据/市场端数据分析/微博&抖音&b站视频数据统计/微博&抖音&b站视频数据统计12-25.xlsx"
```

```{r cross-platform-fans}
da_fan_num <- readxl::read_xlsx(path_wb_bili_xhs, sheet = 1, col_names = TRUE)

# Map short platform labels to (platform, account_name) pairs
mark_account <- function(text) {
  l      <- length(text)
  ans_m  <- matrix(rep("", 2 * l), 2, l)
  ans_m[, text == "微博-七幕"]         <- c("微博",   "七幕人生sevenages")
  ans_m[, text == "微博-法扎"]         <- c("微博",   "音乐剧摇滚莫扎特中文版")
  ans_m[, text == "b站"]               <- c("b站",    "七幕人生sevenages")
  ans_m[, text == "抖音"]              <- c("抖音",   "七幕人生")
  ans_m[, text == "小红书"]            <- c("小红书", "七幕人生")
  ans_m[, text == "小红书-七幕少儿剧团"] <- c("小红书", "七幕少儿剧团")
  unknown <- which(ans_m == "")
  if (length(unknown)) {
    print(unique(text[(unknown + 1) %/% 2]))
    warning("mark_account: unrecognised platform label")
  }
  t(ans_m)
}

# Build weekly follower-count summary (this Monday vs last Monday)
da_fan_num_summary <-
  da_fan_num |>
  arrange(desc(统计时间)) |>
  head(2) |>
  mutate(统计时间 = c("本周一", "上周一")) |>
  pivot_longer(cols = 2:7, names_to = "账号", values_to = "粉丝数") |>
  pivot_wider(names_from = 统计时间, values_from = 粉丝数) |>
  mutate(
    粉丝变化 = 本周一 - 上周一,
    平台     = mark_account(账号)[, 1],
    账号     = mark_account(账号)[, 2]
  ) |>
  dplyr::select(账号, 粉丝数 = 本周一, 上周粉丝数变化 = 粉丝变化, 平台)
```

## Weibo

```{r weibo}
# Helper: convert "1.5W" / "2W" style strings to numeric
mark_num_wb <- function(text) {
  ans <- text
  pat  <- regex("(\\d*?\\.\\d*?)[Ww]$")
  pat2 <- regex("(^\\d*?)[Ww]$")
  ans[str_detect(text, pat)]  <- as.character(as.numeric(str_match(text[str_detect(text, pat)],  pat)[, 2]) * 10000)
  ans[str_detect(text, pat2)] <- as.character(as.numeric(str_match(text[str_detect(text, pat2)], pat2)[, 2]) * 10000)
  as.numeric(ans)
}

read_wb_sheet <- function(sheet_idx, account_name) {
  tmp <- readxl::read_xlsx(path_wb_bili_xhs, sheet = sheet_idx, col_names = TRUE)
  tmp[-1, ] |>
    `colnames<-`(tmp[1, ]) |>
    mutate(
      投稿时间 = as.POSIXct("2023-10-10", tz = "UTC") + (as.numeric(投稿时间) - 45209) * 3600 * 24,
      账号     = account_name
    )
}

da_wb1 <- read_wb_sheet(2, "七幕人生sevenages")
da_wb2 <- read_wb_sheet(3, "音乐剧摇滚莫扎特中文版")

summarise_wb <- function(da_wb, account_name) {
  da_wb |>
    filter(投稿时间 >= date_last_mon, 投稿时间 < date_this_mon) |>
    mutate(阅读数 = mark_num_wb(阅读数)) |>
    summarise(
      内容数目 = n(),
      总观看量 = sum(阅读数),
      总互动量 = as.character(sum(as.numeric(评论数)) + sum(as.numeric(点赞数))),
      总分享   = sum(as.numeric(转发数))
    ) |>
    mutate(平台 = "微博", 账号 = account_name)
}

da_wb_summary <-
  bind_rows(summarise_wb(da_wb1, "七幕人生sevenages"),
            summarise_wb(da_wb2, "音乐剧摇滚莫扎特中文版")) |>
  left_join(da_fan_num_summary, by = c("平台", "账号"))
```

## Bilibili

```{r bilibili}
da_bilibili_tmp <- readxl::read_xlsx(path_wb_bili_xhs, sheet = 4, col_names = TRUE)
da_bilibili <- da_bilibili_tmp[-1, ] |>
  `colnames<-`(da_bilibili_tmp[1, ]) |>
  mutate(投稿时间 = as.POSIXct("2023-10-10", tz = "UTC") + (as.numeric(投稿时间) - 45209) * 3600 * 24)

da_bilibili_summary <-
  da_bilibili |>
  filter(投稿时间 >= date_last_mon, 投稿时间 < date_this_mon) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(as.numeric(播放量)),
    总互动量 = as.character(
      sum(as.numeric(点赞数)) + sum(as.numeric(弹幕数)) +
      sum(as.numeric(评论数)) + sum(as.numeric(收藏数)) + sum(as.numeric(硬币数))
    ),
    总分享 = sum(as.numeric(分享数))
  ) |>
  mutate(账号 = "七幕人生sevenages", 平台 = "b站") |>
  left_join(da_fan_num_summary, by = c("平台", "账号"))
```

## Douyin

```{r douyin}
da_dy_tmp <- readxl::read_xlsx(path_wb_bili_xhs, sheet = 5, col_names = TRUE)
da_dy <- da_dy_tmp[-1, ] |>
  `colnames<-`(da_dy_tmp[1, ]) |>
  mutate(投稿时间 = as.POSIXct("2023-10-10", tz = "UTC") + (as.numeric(投稿时间) - 45209) * 3600 * 24) |>
  filter(!is.na(播放量))

da_dy_summary <-
  da_dy |>
  filter(投稿时间 >= date_last_mon, 投稿时间 < date_this_mon) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(as.numeric(播放量)),
    总互动量 = as.character(
      sum(as.numeric(点赞数)) + sum(as.numeric(评论数)) + sum(as.numeric(收藏))
    ),
    总分享 = sum(as.numeric(转发数))
  ) |>
  mutate(账号 = "七幕人生", 平台 = "抖音") |>
  left_join(da_fan_num_summary, by = c("平台", "账号"))
```

## Xiaohongshu (XHS)

```{r xhs}
# Helper: convert "1.5万" style strings to numeric
mark_num_xhs <- function(text) {
  pat <- regex("(\\d*?\\.\\d*?)万$")
  ans <- text
  ans[str_detect(text, pat)] <- as.character(
    as.numeric(str_match(text[str_detect(text, pat)], pat)[, 2]) * 10000
  )
  as.numeric(ans)
}

# Parse graphic-post data scraped from XHS creator dashboard (HTML/text export)
parse_xhs_posts <- function(lines, col_offsets) {
  id_list <- which(str_detect(lines, "info-text"))[-1]
  as.data.frame(
    str_split_fixed(lines[id_list], regex("<[:print:]*?>"), n = Inf)
  )[, c(3, 5)] |>
    bind_cols(
      as.data.frame(
        str_split_fixed(lines[id_list + 2], regex("<[:print:]*?>"), n = Inf)
      )[, col_offsets]
    )
}

da_red    <- read_lines("E:/实习工作/数据/市场端数据分析/小红书后台数据/小红书创作服务平台-1.txt")
da_red_v1 <- read_lines("E:/实习工作/数据/市场端数据分析/小红书后台数据/小红书创作服务平台-v1.txt")
da_red_v2 <- read_lines("E:/实习工作/数据/市场端数据分析/小红书后台数据/小红书创作服务平台-v2.txt")

# Graphic posts
id_list <- which(str_detect(da_red, "info-text"))[-1]
da_red_edit <- as.data.frame(
  str_split_fixed(da_red[id_list], regex("<[:print:]*?>"), n = Inf)
)[, c(3, 5)] |>
  bind_cols(
    as.data.frame(str_split_fixed(da_red[id_list + 2], regex("<[:print:]*?>"), n = Inf)
    )[, c(8, 10, 17, 19, 25, 27, 35, 37, 44, 46)]
  ) |>
  pivot_wider(names_from = V8,  values_from = V10) |>
  pivot_wider(names_from = V17, values_from = V19) |>
  pivot_wider(names_from = V25, values_from = V27) |>
  pivot_wider(names_from = V35, values_from = V37) |>
  pivot_wider(names_from = V44, values_from = V46) |>
  `colnames<-`(c("标题", "发布时间", colnames(.)[-c(1, 2)])) |>
  mutate(发布时间 = as.POSIXct(发布时间, format = "发布于 %Y-%m-%d", tz = "UTC"))

# Video posts (two batches merged)
parse_xhs_video <- function(lines) {
  id_list <- which(str_detect(lines, "info-text"))[-1]
  as.data.frame(str_split_fixed(lines[id_list], regex("<[:print:]*?>"), n = Inf))[, c(3, 5)] |>
    bind_cols(
      as.data.frame(str_split_fixed(lines[id_list + 2], regex("<[:print:]*?>"), n = Inf)
      )[, c(8, 10, 16, 18, 24, 26, 32, 34, 42, 44, 50, 52, 58, 60, 66, 68)]
    )
}

da_red_v_edit <-
  bind_rows(parse_xhs_video(da_red_v1), parse_xhs_video(da_red_v2)) |>
  pivot_wider(names_from = V8,  values_from = V10) |>
  pivot_wider(names_from = V16, values_from = V18) |>
  pivot_wider(names_from = V24, values_from = V26) |>
  pivot_wider(names_from = V32, values_from = V34) |>
  pivot_wider(names_from = V42, values_from = V44) |>
  pivot_wider(names_from = V50, values_from = V52) |>
  pivot_wider(names_from = V58, values_from = V60) |>
  pivot_wider(names_from = V66, values_from = V68) |>
  `colnames<-`(c("标题", "发布时间", colnames(.)[-c(1, 2)])) |>
  mutate(发布时间 = as.POSIXct(发布时间, format = "发布于 %Y-%m-%d", tz = "UTC"))

# Summarise graphic + video posts for the week
da_xhs_tmp1 <-
  da_red_edit |>
  filter(发布时间 >= date_last_mon, 发布时间 < date_this_mon) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(as.numeric(观看量)),
    总互动量 = as.character(sum(as.numeric(点赞量)) + sum(as.numeric(收藏数)) + sum(as.numeric(评论数))),
    总分享   = sum(as.numeric(分享数))
  ) |>
  mutate(账号 = "七幕人生")

da_xhs_tmp2 <-
  da_red_v_edit |>
  filter(发布时间 >= date_last_mon, 发布时间 < date_this_mon) |>
  mutate(观看量 = mark_num_xhs(观看量)) |>
  summarise(
    内容数目 = n(),
    总观看量 = sum(as.numeric(观看量)),
    总互动量 = as.character(
      sum(as.numeric(点赞量)) + sum(as.numeric(收藏数)) +
      sum(as.numeric(评论数)) + sum(as.numeric(弹幕数))
    ),
    总分享 = sum(as.numeric(分享数))
  ) |>
  mutate(账号 = "七幕人生")

da_xhs_summary <-
  bind_rows(da_xhs_tmp1, da_xhs_tmp2) |>
  summarise(
    内容数目 = sum(内容数目),
    总观看量 = sum(总观看量),
    总互动量 = as.character(sum(as.numeric(总互动量))),
    总分享   = sum(总分享)
  ) |>
  mutate(平台 = "小红书", 账号 = "七幕人生") |>
  left_join(da_fan_num_summary, by = c("平台", "账号")) |>
  full_join(
    da_fan_num_summary |> filter(平台 == "小红书"),
    by = c("平台", "账号", "粉丝数", "上周粉丝数变化")
  )
```

## Enterprise WeChat (企微)

```{r qywx}
path <- list.files("E:/实习工作/数据/市场端数据分析/七幕-企微客服", full.names = TRUE)

da_qywx_fan_num <- map_dfr(path, readxl::read_xlsx) |>
  mutate(
    日期       = as.Date(日期),
    净增客户数 = as.numeric(str_replace(净增客户数, "'", ""))
  ) |>
  arrange(日期)

da_qywx_tmp1 <-
  da_qywx_fan_num |>
  filter(日期 >= date_this_mon - 3600 * 24, 日期 < date_this_mon) |>
  dplyr::select(粉丝数 = 客户总数) |>
  mutate(粉丝数 = as.numeric(粉丝数))

da_qywx_tmp2 <-
  da_qywx_fan_num |>
  filter(日期 >= date_last_mon - 3600 * 24, 日期 < date_last_mon) |>
  dplyr::select(粉丝数_prev = 客户总数) |>
  mutate(粉丝数_prev = as.numeric(粉丝数_prev)) |>
  mutate(上周粉丝数变化 = da_qywx_tmp1$粉丝数 - 粉丝数_prev) |>
  dplyr::select(上周粉丝数变化)

da_qywx_summary <-
  da_qywx_tmp1 |>
  bind_cols(da_qywx_tmp2) |>
  mutate(账号 = "客服-企微", 平台 = "微信")
```

## Consolidated Cross-Platform Summary

```{r channel-attribution}
# Map referral (渠道明细) labels to the owning social account
mark_zhanghao_da <- function(text) {
  l     <- length(text)
  ans_m <- matrix(rep("无", 2 * l), 2, l)

  list_dyh <- c(
    unique(text[str_sub(text, 1, 2) == "推文"]),
    "订阅号-MOR", "订阅号-MA",
    "公众号展示-上海", "公众号展示-北京", "公众号展示-深圳",
    "订阅号展示-MA", "订阅号展示-MOR"
  )
  list_fwh <- c(
    unique(text[str_sub(text, 1, 5) == "服务号推文"]),
    "服务号-MOR", "服务号-MA", "服务号展示-MA", "服务号展示-MOR"
  )
  list_wb <- unique(text[str_sub(text, 1, 2) == "微博"])
  list_qw <- c(
    unique(text[is.element(str_sub(text, 1, 5), c("企微朋友圈", "培训企微群", "小七点对点", "培训点对点"))]),
    unique(text[str_sub(text, 1, 3) == "企微群"]),
    unique(text[str_sub(text, 1, 6) == "小七自动回复"]),
    unique(text[str_sub(text, 1, 8) == "培训-企微朋友圈"])
  )

  ans_m[, is.element(text, list_dyh)] <- c("七幕-订阅号",    "微信")
  ans_m[, is.element(text, list_fwh)] <- c("七幕人生-服务号", "微信")
  ans_m[, is.element(text, list_qw)]  <- c("客服-企微",       "微信")
  ans_m[, is.element(text, list_wb)]  <- c("七幕人生sevenages", "微博")

  t(ans_m)
}

da_for_market_summary <-
  da_for_market |>
  filter(下单时间 >= date_last_mon, 下单时间 < date_this_mon) |>
  mutate(
    账号 = mark_zhanghao_da(渠道明细)[, 1],
    平台 = mark_zhanghao_da(渠道明细)[, 2]
  ) |>
  filter(账号 != "无") |>
  group_by(平台, 账号) |>
  summarise(
    售票数 = sum(张数),
    收入   = sum(实收),
    .groups = "drop"
  )
```

```{r final-summary}
# Full cross-platform weekly report table
bind_rows(
  da_wx_summary,
  da_wx_video_summary,
  da_px_summary,
  da_px_video_summary,
  da_qywx_summary,
  da_wb_summary,
  da_dy_summary,
  da_xhs_summary,
  da_bilibili_summary
) |>
  full_join(da_for_market_summary, by = c("账号", "平台")) |>
  relocate(平台, 账号) |>
  dplyr::select(-平台) |>
  mutate(across(c(售票数, 收入, 内容数目, 总观看量, 总互动量, 总分享),
                ~ coalesce(as.character(.), "-")))
```
